---
title: "Homework 5"
author: Nancy Fang (nf2466)
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1
Read in the data

```{r}
homicide_df = 
  read.csv("data/homicide-data.csv")%>%
  mutate(
    city_state = str_c(city, state, sep="_"),
    resolved = case_when(disposition == "Closed by arrest" ~"solved",
                         disposition == "Closed without arrest" ~"unsolved",
                         disposition == "Open/No arrest" ~"unsolved"))%>%
  select(city_state, resolved)
  
```

The raw data is a CSV file that contains several variables, including the report date, first and last name of the victims, race, age, sex, city, state, location (latitude and longitude) and disposition of the case. The original dataset contains `r nrow(homicide_df)` rows. 

Aggregate data:

```{r}
homicide_sum = 
  homicide_df %>%
    group_by(city_state)%>%
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )%>%
  filter(city_state != "Tulsa_AL")
```
We know that there are only 50 cities included in the data set, yet the original dataset had 51 cities. When we arranged the `city_state` variable by total homicides, we saw that Tulsa_AL only had one total homicide, which likely was an input error.

Single prop test for Baltimore, MD:

```{r}
  baltimore_prop = 
  prop.test(homicide_sum %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved),
            homicide_sum %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)
  ) %>% 
  broom::tidy() %>%
  select(estimate, conf.low, conf.high)

```
Prop.test for each of the cities in your dataset:

```{r}
results_df = 
  homicide_sum %>%
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  )%>%
  select(-prop_tests)%>%
  unnest(tidy_tests)%>%
  select(city_state,estimate, conf.low, conf.high)

results_df %>%
  knitr::kable()

```

Plot that shows the estimates and CIs for each city:

```{r}
unsolved_plot = 
  results_df %>%
  mutate(city_state = fct_reorder(city_state,estimate)) %>%
  ggplot(aes(x = city_state, y = estimate)) +
    geom_point() +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

unsolved_plot
```



